Covid-19 A Spatio-Temporal Investigation.

### 2021-01-03 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 At the end of 2019, the situation of infections by Covid-19 *(Sars-Cov-2)* was already a cause for concern, and it was considered an epidemic in the city of Wuhan in China $\!\!^1$, although it was difficult to identify the virus' origin, it's known that the Severe Acute Respiratory Syndrome *(SARS)* and the Middle East respiratory syndrome *(MERS)* usually need intermediate hosts $\!\!^2$, there is a possibility that bats and pangolins were the first carriers. After several public organizations called for caution relating to Covid-19, on March 12 of 2020 the pandemic state was recognized by the World Health Organization *(WHO)* $\!\!^3$.

 No final de 2019, o estado de contágio pela Covid-19 (Sars-CoV-2) já era considerado como epidêmico na cidade de Wuhan na China $\!\!^1$, apesar da dificuldade de identificar a origem do vírus, é possível que tanto pangolim como o morcego tenham sido hospedeiros iniciais, visto que tanto a síndrome respiratória aguda grave *(SARS)* quanto a síndrome respiratória do Oriente Médio *(MERS)* geralmente passam por hospedeiros intermediários $\!\!^2$. Apesar de anteriormente diversos orgãos públicos recomendarem cautela em relação a Covid-19, em 12 de março de 2020 o estado de pandemia foi reconhecido pela Organização Mundial da Saúde (OMS) $\!\!^3$.

>>>>

 At the end of 2019, the situation of infections by Covid-19 *(Sars-Cov-2)* was already a cause for concern, and it was considered an epidemic in the city of Wuhan in China $\!\!^1$, although it was difficult to identify the virus' origin, it's known that the Severe Acute Respiratory Syndrome *(SARS)* and the Middle East Respiratory Syndrome *(MERS)* usually need intermediate hosts $\!\!^2$, there is a possibility that bats and pangolins were the first carriers. After several public organizations called for caution relating to Covid-19, on March 12 of 2020 the pandemic state was recognized by the World Health Organization *(WHO)* $\!\!^3$.

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the spatio-temporal aspects of the pandemic should be conducted, by evaluating the political measures adopted by different countries to contain infections accordingly to time.
